---
title: "R Notebook"
output: html_notebook
---

Read in CSV data for tiles that will be used
```{r}
S2_data<- read.csv("Z:\\Brittany\\Documents\\ProjectWork\\Ancillary\\s2_alltiles_query.csv")
L8_data<- read.csv("Z:\\Brittany\\Documents\\ProjectWork\\Ancillary\\all_L8_tiles.csv") %>%
  filter(SceneCloudCover <= 50)
```
this is a chunk

Determine unique values for S2
```{r error= TRUE}
query2<- S2_data %>%
    filter(cloudcoverpercentage <= 50) %>%
    mutate(acquisitionDate = ymd_hms(gsub("T","",datatakesensingstart)),
           Year = year(acquisitionDate),
           Month = month(acquisitionDate),
           uniq_ID = paste(acquisitionDate, tileid))
unique(query2$uniq_ID)
uniq_sen2<- query2[!duplicated(query2$uniq_ID),]
uniq_sen2
```

Prepare/tidy data to create data availability graph for S2
```{r}
sent_graph<- uniq_sen2%>%
  rename(Cloud.Cover = cloudcoverpercentage) %>%
  mutate(Doy = as.factor(strftime(acquisitionDate, format = "%j")))
##Check data
sent_graph
```

Write CSV
```{r}
write.csv(sent_graph, "Z:\\Brittany\\Documents\\ProjectWork\\Ancillary\\tally_S2_dataavail.csv")
```

Plot data availability for Sentinel 2 for CA lakes
```{r}
ggplot(sent_graph) +
  geom_tile(aes(x = Doy, y = Year, fill = Cloud.Cover), width = 1.5, size = 0.5) +
  scale_y_continuous(breaks = c(2015:2018))  + 
  scale_x_discrete(breaks = c("0", "100", "200", "300"))  + 
  ggtitle("Sentinel-2 Satellite Cloud Cover for California Lakes") + 
  ylab("Year") + 
  xlab("Day of Year") + theme_bw() + scale_fill_continuous(type = "viridis")
```

Look at availability for each tile for Sentinel-2 by year and month

```{r}
sent_graph%>%
  group_by(Year, Month, tileid) %>%
  tally()
```

Determine unique values for L8
```{r}
uniq_l8<- L8_data[!duplicated(L8_data$displayId),] 
uniq_l8

#total 3464
```

Prepare/tidy data to create data availability graph for L8
```{r}
l8_graph<- uniq_l8%>%
  rename(Cloud.Cover = SceneCloudCover) %>%
  mutate(Doy = as.factor(strftime(acquisitionDate, format = "%j")),
         Year = year(acquisitionDate),
         Month = month(acquisitionDate),
         Path_Row = paste(WRSPath, WRSRow, sep = "_"))
##Check data
l8_graph 
```

Write CSV
```{r}
write.csv(l8_graph, "Z:\\Brittany\\Documents\\ProjectWork\\Data_Avail_CSV\\tally_L8_dataavail.csv")
```

Plot data availability for L8 for CA lakes
```{r}
ggplot(l8_graph) +
  geom_tile(aes(x = Doy, y = Year, fill = Cloud.Cover), width = 1.5, size = 0.5) +
  scale_y_continuous(breaks = c(2015:2018))  + 
  scale_x_discrete(breaks = c("0", "100", "200", "300"))  + 
  ggtitle("Landsat-8 Satellite Cloud Cover for California Lakes") + 
  ylab("Year") + 
  xlab("Day of Year") + theme_bw() + scale_fill_continuous(type = "viridis")
```

Look at availability for each tile for Sentinel-2 by year and month
```{r}
l8_graph%>%
  group_by(Year, Month, Path_Row) %>%
  tally()
```