---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Read in required packages

```{r}
library(ggplot2)
library(dplyr)
```


Read in CSVs for graph and to tally tiles for each satellite
```{r}
graph_s2<- read.csv("Z:\\Brittany\\Documents\\ProjectWork\\Data_Avail_CSV\\tally_S2_dataavail.csv")
graph_L8<- read.csv("Z:\\Brittany\\Documents\\ProjectWork\\Data_Avail_CSV\\tally_L8_dataavail.csv") %>%
  filter(Cloud.Cover <= 50)
```

Create S2 data availability graph
```{r}
ggplot(graph_s2) +
  geom_tile(aes(x = Doy, y = Year, fill = Cloud.Cover), width = 1.5, size = 0.5) +
  scale_y_continuous(breaks = c(2015:2018))  + 
  scale_x_discrete(breaks = c("0", "100", "200", "300"))  + 
  ggtitle("Sentinel-2 Satellite Cloud Cover for California Lakes") + 
  ylab("Year") + 
  xlab("Day of Year") + theme_bw() + scale_fill_continuous(type = "viridis")
```
Overall tally for Sentinel 2
```{r}
graph_s2%>%
  group_by(Year, Month, tileid) %>%
  tally()
```

Create bins for 0-50% cloud cover by 10% increments
```{r}
mylabels<- c("0-10", "10-20", "20-30", "30-40", "40-50")
bins_s2 <- graph_s2%>%
  mutate(Cloud_Range = cut(Cloud.Cover, breaks = c(-0.001,10,20,30,40,50) , labels = mylabels)) %>%
  dplyr::select(c("title", "Cloud.Cover", "tileid", "Year", "Month", "Cloud_Range"))
###Note that breaks begin with -0.001; it is because it would leave "NA" for all 0 values
bins_s2
```

Tally for all bin values for S2
```{r}
bins_s2 %>%
  group_by(Year, Month, tileid, Cloud_Range) %>%
  tally()
```
Tally for cloud cover ranging 0-10%: S2
```{r}
less_10S2<- bins_s2 %>%
  filter(Cloud_Range == "0-10")
less_10S2 %>%
  group_by(Year, Month, tileid, Cloud.Cover) %>%
  tally()
```

Tally for range from 10.01-20%: S2
```{r}
from10_20s2<- bins_s2 %>%
  filter(Cloud_Range == "10-20")
from10_20s2 %>%
  group_by(Year, Month, tileid, Cloud.Cover) %>%
  tally()
```

Tally for range from 20.01-30%: L8
```{r}
from_20to30s2<- bins_s2 %>%
  filter(Cloud_Range == "20-30")

from_20to30s2 %>%
  group_by(Year, Month, tileid, Cloud.Cover) %>%
  tally()
```

Tally for range from 30.01-40%: S2
```{r}
from_30to40s2<- bins_s2 %>%
  filter(Cloud_Range == "30-40")

from_30to40s2 %>%
  group_by(Year, Month, tileid, Cloud.Cover) %>%
  tally()
```

Tally for range from 40.01-50%: S2
```{r}
from_40to50s2<- bins_s2 %>%
  filter(Cloud_Range == "40-50")

from_40to50s2 %>%
  group_by(Year, Month, tileid, Cloud.Cover) %>%
  tally()
```



Create L8 data availability graph
```{r}
ggplot(graph_L8) +
  geom_tile(aes(x = Doy, y = Year, fill = Cloud.Cover), width = 1.5, size = 0.5) +
  scale_y_continuous(breaks = c(2015:2018))  + 
  scale_x_discrete(breaks = c("0", "100", "200", "300"))  + 
  ggtitle("Landsat-8 Satellite Cloud Cover for California Lakes") + 
  ylab("Year") + 
  xlab("Day of Year") + theme_bw() + scale_fill_continuous(type = "viridis")
```

Overall tally for Landsat 8 
```{r}
graph_L8%>%
  group_by(Year, Month, Path_Row) %>%
  tally()
```

Create bins for 0-50% cloud cover by 10% increments
```{r}
mylabels<- c("0-10", "10-20", "20-30", "30-40", "40-50")
bins_l8 <- graph_L8%>%
  mutate(Cloud_Range = cut(Cloud.Cover, breaks = c(-0.001,10,20,30,40,50) , labels = mylabels)) %>%
  dplyr::select(c("path", "row", "landsat_product_id", "Cloud.Cover", "Path_Row", "Year", "Month", "Cloud_Range"))
###Note that breaks begin with -0.001; it is because it would leave "NA" for all 0 values
bins_l8 
```

Tally for all bin values
```{r}
bins_l8 %>%
  group_by(Year, Month, Path_Row, Cloud_Range) %>%
  tally()
```
Tally for cloud cover ranging 0-10%
```{r}
less_10<- bins_l8 %>%
  filter(Cloud_Range == "0-10")
less_10 %>%
  group_by(Year, Month, Path_Row, Cloud.Cover) %>%
  tally()
```

Tally for range from 10.01-20%: L8
```{r}
from10_20<- bins_l8 %>%
  filter(Cloud_Range == "10-20")
from10_20 %>%
  group_by(Year, Month, Path_Row, Cloud.Cover) %>%
  tally()
```

Tally for range from 20.01-30%: L8
```{r}
from_20to30<- bins_l8 %>%
  filter(Cloud_Range == "20-30")

from_20to30 %>%
  group_by(Year, Month, Path_Row, Cloud.Cover) %>%
  tally()
```

Tally for range from 30.01-40%: L8
```{r}
from_30to40<- bins_l8 %>%
  filter(Cloud_Range == "30-40")

from_30to40 %>%
  group_by(Year, Month, Path_Row, Cloud.Cover) %>%
  tally()
```

Tally for range from 40.01-50%: L8
```{r}
from_40to50<- bins_l8 %>%
  filter(Cloud_Range == "40-50")

from_40to50 %>%
  group_by(Year, Month, Path_Row, Cloud.Cover) %>%
  tally()
```
